### 2020-07-01 chapters/validation.tex
PDF images

All the synthetic datasets used throughout this Section are a time-series where at each time-step we sample uniformly from a fixed distribution, \textit{i.e.} there are no time correlations in the used datasets. The reference dataset R1 used in this first experiment contained a single feature that followed a normal distribution with mean $\mu=10$ and standard deviation $\sigma=2$ for the 5 million rows of the dataset. Figure \ref{fig:timeseries-r1} shows the time-series of the single feature in dataset R1. The dataset processed in the streaming phase (\textit{i.e.} the target dataset) was generated with a size of 5 million events and a single feature. For the first half, \textit{i.e.}, for the first 2.5 million events, the feature followed a normal distribution with mean $\mu=10$ and standard deviation $\sigma=2$, like the reference dataset. For the other half, we changed the generating distribution to be a continuous uniform one with lower bound $a=100$ and upper bound $b=200$. Figure \ref{fig:timeseries-t1} shows the time-series of the single feature in the target dataset T1 where we see the abrupt change in feature values.
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/01-reference.png}
  \captionof{figure}{Time-series for dataset R1}
  \label{fig:timeseries-r1}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/01-target.png}
  \captionof{figure}{Time-series for dataset T1}
  \label{fig:timeseries-t1}
\end{minipage}
\end{center}

@@

From a functional point of view, were we able to detect the abrupt change introduced in the target dataset T1? Recall that from the 2.5 millionth event forward we change the distribution from a gaussian to an uniform one (Figure \ref{fig:timeseries-t1}). Figure \ref{fig:JSD-signal-01} shows the distance (JSD) values computed during streaming at each event of the 5 million events from dataset T1, using the outputs from the batch phase of experiment 01. We clearly see a change in JSD values, and we move from values close to 0 to values close to 1 (or even 1). Figure \ref{fig:JSD-signal-zoom-01} shows the same signal but for the first half of the streaming period (essentially a zoom-in). We see our JSD values before the change were very low (magnitudes of $10^{-2}$).
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-625.png}
  \captionof{figure}{JSD signal and threshold}
  \label{fig:JSD-signal-01}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-zoom-625.png}
  \captionof{figure}{Zoomed in JSD signal and threshold}
  \label{fig:JSD-signal-zoom-01}
\end{minipage}
\end{center}
However, the change in JSD value is very abrupt as well. Almost instantly we go from close to 0 values to 1. We also had some false-positives, \textit{i.e.}, some JSD values above the threshold. This indicates to us that the window used is too small and sensitive to small changes, or that we can choose a more strict threshold.

@@

Figure \ref{fig:JSD-signal-02} shows the JSD signal during streaming for dataset T1, using the outputs from the batch phase of experiment 02. Again, we see a change in signal from the middle of the streaming period forward. Figure \ref{fig:JSD-signal-zoom-02} shows the same signal for the first half of the streaming period.
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-62500.png}
  \captionof{figure}{JSD signal and threshold}
  \label{fig:JSD-signal-02}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-zoom-62500.png}
  \captionof{figure}{Zoomed in JSD signal and threshold}
  \label{fig:JSD-signal-zoom-02}
\end{minipage}
\end{center}
Notice that this time the growth of our signal is slower. Notice also that we do not have false positives in the first half of the signal. This is because we use a larger window, which means each event has a smaller contribution to the aggregation state. Hence, outliers will have less impact on the aggregation and corresponding signal value.

In experiment 03, we increase the sampling and target windows size once again, this time four times larger than in experiment 02. We would expect an even smoother growth of our signal and, again, no false positives. And indeed, judging by the corresponding signal computation and zoom-in, Figures \ref{fig:JSD-signal-03} and \ref{fig:JSD-signal-zoom-03}, respectively, the signal looks smoother and we see no false positives.
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-250000.png}
  \captionof{figure}{JSD signal and threshold}
  \label{fig:JSD-signal-03}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-zoom-250000.png}
  \captionof{figure}{Zoomed in JSD signal and threshold}
  \label{fig:JSD-signal-zoom-03}
\end{minipage}
\end{center}

\subsubsection{Multiple distribution changes}
In this experiment, we wanted to see how our signal behaved when there were multiple change points, where each gaussian distribution was a scaled down version of the previous one. Figure \ref{fig:timeseries-r2} shows the time-series for the reference dataset R2 used in this experiment. It contained 5 million events with a single feature following a gaussian distribution with mean $\mu=100$ and standard deviation $\sigma=50$. The time-series for target dataset T2 is shown in Figure \ref{fig:timeseries-t2}. Notice that we change distributions at 2, 3 and 4 millionth events. Notice also that each subsequent distribution produces values whose domain is a subset of the previous distribution.
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-r2.png}
  \captionof{figure}{Time-series for dataset R2}
  \label{fig:timeseries-r2}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-t2.png}
  \captionof{figure}{Time-series for dataset T2}
  \label{fig:timeseries-t2}
\end{minipage}
\end{center}

@@

In this experiment, we used a half-life $n_{1/2}=62500$ and corresponding sample size of 250,000 events, like in the previous Section' experiment 02. Figure \ref{fig:JSD-signal-test02} shows the computed JSD signal for the target dataset and Figure \ref{fig:JSD-signal-zoom-test02} zooms in on the first 2 millionth events, before any distribution is changed. We observe that once again we have no false positives in the first 2 million events, which is ideal. 
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-test02.png}
  \captionof{figure}{JSD signal and threshold}
  \label{fig:JSD-signal-test02}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-zoom-test02.png}
  \captionof{figure}{Zoomed in JSD signal and threshold}
  \label{fig:JSD-signal-zoom-test02}
\end{minipage}
\end{center}
Furthermore, we observe that the computed JSD signal varies accordingly with the changes in distribution. Despite us changing the distributions to subsets of the previous ones to try and deceive our method, our signal accurately represents these changes. In Figure \ref{fig:JSD-signal-test02}, we see several growth points that correspond to the points where the generating gaussian distribution parameters changed. Hence, we are able to detect changes in distribution parameter changes and quantify how big the change is (the closer to 1 our signal is).

\subsubsection{Multiple distribution changes, each a superset of the previous one}
In this experiment, we wanted to do the reverse of the previous one. In this one, there are multiple change points but each new distribution spans a domain that is a superset of the previous one. Figure \ref{fig:timeseries-r3} shows the reference period used, with 5 million events and one feature following a gaussian distribution of mean $\mu=100$ and standard deviation $\sigma=10$. Figure \ref{fig:timeseries-t3} shows the target period used, also with 5 million events and one feature. Like in the previous experiment, we change distributions at the 2, 3 and 4 millionth event mark. On the other hand, unlike the previous experiment, we now make subsequent distributions cover the previous ones. We change the reference gaussian used with mean $\mu=100$ and standard deviation $\sigma=10$ at the 2, 3 and 4 millionth mark, to use standard deviations $\sigma=30$, $\sigma=40$ and $\sigma=50$, respectively.
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-r3.png}
  \captionof{figure}{Time-series for dataset R3}
  \label{fig:timeseries-r3}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1.2\linewidth]{figures/timeseries-t3.png}
  \captionof{figure}{Time-series for dataset T3}
  \label{fig:timeseries-t3}
\end{minipage}
\end{center}

Figure \ref{fig:JSD-signal-test03} shows the JSD signal for the target dataset in this experiment. Once again, we were able to detect the changes introduced at the 2, 3 and 4 millionth events. We are also able to identify bigger distribution changes, relative to the reference, by observing bigger JSD values. Figure \ref{fig:JSD-signal-zoom-test03} shows a zoomed in portion of the original signal, where we can verify that there are no false positives.
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-test03.png}
  \captionof{figure}{JSD signal and threshold}
  \label{fig:JSD-signal-test03}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-zoom-test03.png}
  \captionof{figure}{Zoomed in JSD signal and threshold}
  \label{fig:JSD-signal-zoom-test03}
\end{minipage}
\end{center}

@@

In this experiment, we used reference dataset R4 (Figure \ref{fig:timeseries-r4}) and target dataset T4 (Figure \ref{fig:timeseries-t4}). 
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-r4.png}
  \captionof{figure}{Time-series for dataset R4}
  \label{fig:timeseries-r4}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-t4.png}
  \captionof{figure}{Time-series for dataset T4}
  \label{fig:timeseries-t4}
\end{minipage}
\end{center}

@@

\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-test04.png}
  \captionof{figure}{JSD signal and threshold}
  \label{fig:JSD-signal-test04}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-zoom-test04.png}
  \captionof{figure}{Zoomed in JSD signal and threshold}
  \label{fig:JSD-signal-zoom-test04}
\end{minipage}
\end{center}

@@

We used the reference dataset R5 (Figure \ref{fig:timeseries-r5}) which had 5 million events, with a single-feature that followed a gaussian with  $\mu=100$ and $\sigma=10$. Our target dataset T5 is represented in Figure \ref{fig:timeseries-t5}. For the first 2 million events, the generating distribution used was similar to the one used in the reference dataset, a gaussian with $\mu=100$ and $\sigma=10$. However, at the 2 millionth event, we change the gaussian standard deviation to $\sigma=30$. Then, at the 4 millionth event, we change the distribution type. We use an uniform distribution with lower bound $a=80$ and upper bound $b=120$. Note in Figure \ref{fig:timeseries-t5} that this last portion resembles the first one, the reference.
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-r5.png}
  \captionof{figure}{Time-series for dataset R5}
  \label{fig:timeseries-r5}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-t5.png}
  \captionof{figure}{Time-series for dataset T5}
  \label{fig:timeseries-t5}
\end{minipage}
\end{center}

Let's take a look at the signal computed for the target period. Figure \ref{fig:JSD-signal-test05} shows us the JSD signal for dataset T5 \ref{fig:timeseries-t5}. As expected, we see a rapid growth of JSD value after the 2 millionth event, when we change the Gaussian parameters. We then change the distribution type, from a gaussian to a uniform one. Despite the latter having a domain contained within the former, we see that our signal is accurate and does not drop below the alert threshold. This is still a different distribution that we want to alert. Figure \ref{fig:JSD-signal-zoom-test05} is a zoom in of the first 2 millionth events and once again we have no false positives.
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-test05.png}
  \captionof{figure}{Distance (JSD) signal and threshold}
  \label{fig:JSD-signal-test05}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-zoom-test05.png}
  \captionof{figure}{Zoomed in distance (JSD) signal and threshold}
  \label{fig:JSD-signal-zoom-test05}
\end{minipage}
\end{center}

@@

\begin{figure}[!htb] 
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-r6-x1.png} 
    \caption{Feature x1 reference time-series} 
    \label{fig:timeseries-r6-x1} 
    \vspace{4ex}
  \end{minipage}%%
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-r6-x2.png} 
    \caption{Feature x2 reference time-series} 
    \label{fig:timeseries-r6-x2} 
    \vspace{4ex}
  \end{minipage} 
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-r6-x3.png} 
    \caption{Feature x3 reference time-series} 
    \label{fig:timeseries-r6-x3} 
    \vspace{4ex}
  \end{minipage}%% 
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-r6-x4.png} 
    \caption{Feature x4 reference time-series} 
    \label{fig:timeseries-r6-x4} 
    \vspace{4ex}
  \end{minipage} 
\end{figure}

@@

\begin{figure}[!htb] 
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-t6-x1.png} 
    \caption{Feature x1 target time-series} 
    \label{fig:timeseries-t6-x1} 
    \vspace{4ex}
  \end{minipage}%%
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-t6-x2.png} 
    \caption{Feature x2 target time-series} 
    \label{fig:timeseries-t6-x2} 
    \vspace{4ex}
  \end{minipage} 
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-t6-x3.png} 
    \caption{Feature x3 target time-series} 
    \label{fig:timeseries-t6-x3} 
    \vspace{4ex}
  \end{minipage}%% 
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-t6-x4.png} 
    \caption{Feature x4 target time-series} 
    \label{fig:timeseries-t6-x4} 
    \vspace{4ex}
  \end{minipage} 
\end{figure}

>>>>

All the synthetic datasets used throughout this Section are a time-series where at each time-step we sample uniformly from a fixed distribution, \textit{i.e.} there are no time correlations in the used datasets. The reference dataset R1 used in this first experiment contained a single feature that followed a normal distribution with mean $\mu=10$ and standard deviation $\sigma=2$ for the 5 million rows of the dataset. Figure \ref{fig:timeseries-r1} shows the time-series of the single feature in dataset R1. The dataset processed in the streaming phase (\textit{i.e.} the target dataset) was generated with a size of 5 million events and a single feature. For the first half, \textit{i.e.}, for the first 2.5 million events, the feature followed a normal distribution with mean $\mu=10$ and standard deviation $\sigma=2$, like the reference dataset. For the other half, we changed the generating distribution to be a continuous uniform one with lower bound $a=100$ and upper bound $b=200$. Figure \ref{fig:timeseries-t1} shows the time-series of the single feature in the target dataset T1 where we see the abrupt change in feature values.
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/01-reference.pdf}
  \captionof{figure}{Time-series for dataset R1}
  \label{fig:timeseries-r1}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/01-target.pdf}
  \captionof{figure}{Time-series for dataset T1}
  \label{fig:timeseries-t1}
\end{minipage}
\end{center}

@@

From a functional point of view, were we able to detect the abrupt change introduced in the target dataset T1? Recall that from the 2.5 millionth event forward we change the distribution from a gaussian to an uniform one (Figure \ref{fig:timeseries-t1}). Figure \ref{fig:JSD-signal-01} shows the distance (JSD) values computed during streaming at each event of the 5 million events from dataset T1, using the outputs from the batch phase of experiment 01. We clearly see a change in JSD values, and we move from values close to 0 to values close to 1 (or even 1). Figure \ref{fig:JSD-signal-zoom-01} shows the same signal but for the first half of the streaming period (essentially a zoom-in). We see our JSD values before the change were very low (magnitudes of $10^{-2}$).
\begin{figure}[!htb]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-625.pdf}
  \caption{For the whole time-series}
  \label{fig:JSD-signal-01}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-zoom-625.pdf}
  \caption{Zoom in on the first 2.5 million events}
  \label{fig:JSD-signal-zoom-01}
\end{subfigure}
\caption{Experiment 01: JSD signal and threshold}
\end{figure}

However, the change in JSD value is very abrupt as well. Almost instantly we go from close to 0 values to 1. We also had some false-positives, \textit{i.e.}, some JSD values above the threshold. This indicates to us that the window used is too small and sensitive to small changes, or that we can choose a more strict threshold.

@@

Figure \ref{fig:JSD-signal-02} shows the JSD signal during streaming for dataset T1, using the outputs from the batch phase of experiment 02. Again, we see a change in signal from the middle of the streaming period forward. Figure \ref{fig:JSD-signal-zoom-02} shows the same signal for the first half of the streaming period.
\begin{figure}[!htb]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-62500.pdf}
  \caption{For the whole time-series}
  \label{fig:JSD-signal-02}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-zoom-62500.pdf}
  \caption{Zoom in on the first 2.5 million events}
  \label{fig:JSD-signal-zoom-02}
\end{subfigure}
\caption{Experiment 02: JSD signal and threshold}
\end{figure}
Notice that this time the growth of our signal is slower. Notice also that we do not have false positives in the first half of the signal. This is because we use a larger window, which means each event has a smaller contribution to the aggregation state. Hence, outliers will have less impact on the aggregation and corresponding signal value.

In experiment 03, we increase the sampling and target windows size once again, this time four times larger than in experiment 02. We would expect an even smoother growth of our signal and, again, no false positives. And indeed, judging by the corresponding signal computation and zoom-in, Figures \ref{fig:JSD-signal-03} and \ref{fig:JSD-signal-zoom-03}, respectively, the signal looks smoother and we see no false positives.
\begin{figure}[!htb]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-250000.pdf}
  \caption{For the whole time-series}
  \label{fig:JSD-signal-03}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-zoom-250000.pdf}
  \caption{Zoom in on the first 2.5 million events}
  \label{fig:JSD-signal-zoom-03}
\end{subfigure}
\caption{Experiment 03: JSD signal and threshold}
\end{figure}

\subsubsection{Multiple distribution changes}
In this experiment, we wanted to see how our signal behaved when there were multiple change points, where each gaussian distribution was a scaled down version of the previous one. Figure \ref{fig:timeseries-r2} shows the time-series for the reference dataset R2 used in this experiment. It contained 5 million events with a single feature following a gaussian distribution with mean $\mu=100$ and standard deviation $\sigma=50$. The time-series for target dataset T2 is shown in Figure \ref{fig:timeseries-t2}. Notice that we change distributions at 2, 3 and 4 millionth events. Notice also that each subsequent distribution produces values whose domain is a subset of the previous distribution.
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-r2.pdf}
  \captionof{figure}{Time-series for dataset R2}
  \label{fig:timeseries-r2}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-t2.pdf}
  \captionof{figure}{Time-series for dataset T2}
  \label{fig:timeseries-t2}
\end{minipage}
\end{center}

@@

In this experiment, we used a half-life $n_{1/2}=62500$ and corresponding sample size of 250,000 events, like in the previous Section' experiment 02. Figure \ref{fig:JSD-signal-test02} shows the computed JSD signal for the target dataset and Figure \ref{fig:JSD-signal-zoom-test02} zooms in on the first 2 millionth events, before any distribution is changed. We observe that once again we have no false positives in the first 2 million events, which is ideal. 
\begin{figure}[!htb]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-test02.pdf}
  \caption{For the whole time-series}
  \label{fig:JSD-signal-test02}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-zoom-test02.pdf}
  \caption{Zoom in on the first 2 million events}
  \label{fig:JSD-signal-zoom-test02}
\end{subfigure}
\caption{JSD signal and threshold}
\end{figure}
Furthermore, we observe that the computed JSD signal varies accordingly with the changes in distribution. Despite us changing the distributions to subsets of the previous ones to try and deceive our method, our signal accurately represents these changes. In Figure \ref{fig:JSD-signal-test02}, we see several growth points that correspond to the points where the generating gaussian distribution parameters changed. Hence, we are able to detect changes in distribution parameter changes and quantify how big the change is (the closer to 1 our signal is).

\subsubsection{Multiple distribution changes, each a superset of the previous one}
In this experiment, we wanted to do the reverse of the previous one. In this one, there are multiple change points but each new distribution spans a domain that is a superset of the previous one. Figure \ref{fig:timeseries-r3} shows the reference period used, with 5 million events and one feature following a gaussian distribution of mean $\mu=100$ and standard deviation $\sigma=10$. Figure \ref{fig:timeseries-t3} shows the target period used, also with 5 million events and one feature. Like in the previous experiment, we change distributions at the 2, 3 and 4 millionth event mark. On the other hand, unlike the previous experiment, we now make subsequent distributions cover the previous ones. We change the reference gaussian used with mean $\mu=100$ and standard deviation $\sigma=10$ at the 2, 3 and 4 millionth mark, to use standard deviations $\sigma=30$, $\sigma=40$ and $\sigma=50$, respectively.
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-r3.pdf}
  \captionof{figure}{Time-series for dataset R3}
  \label{fig:timeseries-r3}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-t3.pdf}
  \captionof{figure}{Time-series for dataset T3}
  \label{fig:timeseries-t3}
\end{minipage}
\end{center}

Figure \ref{fig:JSD-signal-test03} shows the JSD signal for the target dataset in this experiment. Once again, we were able to detect the changes introduced at the 2, 3 and 4 millionth events. We are also able to identify bigger distribution changes, relative to the reference, by observing bigger JSD values. Figure \ref{fig:JSD-signal-zoom-test03} shows a zoomed in portion of the original signal, where we can verify that there are no false positives.
\begin{figure}[!htb]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-test03.pdf}
  \caption{For the whole time-series}
  \label{fig:JSD-signal-test03}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-zoom-test03.pdf}
  \caption{Zoom in on the first 2 million events}
  \label{fig:JSD-signal-zoom-test03}
\end{subfigure}
\caption{JSD signal and threshold}
\end{figure}

@@

In this experiment, we used reference dataset R4 (Figure \ref{fig:timeseries-r4}) and target dataset T4 (Figure \ref{fig:timeseries-t4}). 
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-r4.pdf}
  \captionof{figure}{Time-series for dataset R4}
  \label{fig:timeseries-r4}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-t4.pdf}
  \captionof{figure}{Time-series for dataset T4}
  \label{fig:timeseries-t4}
\end{minipage}
\end{center}

@@

\begin{figure}[!htb]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-test04.pdf}
  \captionof{figure}{JSD signal and threshold}
  \label{fig:JSD-signal-test04}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-zoom-test04.pdf}
  \caption{Zoom in on the first 2 million events}
  \label{fig:JSD-signal-zoom-test04}
\end{subfigure}
\caption{JSD signal and threshold}
\end{figure}

@@

We used the reference dataset R5 (Figure \ref{fig:timeseries-r5}) which had 5 million events, with a single-feature that followed a gaussian with  $\mu=100$ and $\sigma=10$. Our target dataset T5 is represented in Figure \ref{fig:timeseries-t5}. For the first 2 million events, the generating distribution used was similar to the one used in the reference dataset, a gaussian with $\mu=100$ and $\sigma=10$. However, at the 2 millionth event, we change the gaussian standard deviation to $\sigma=30$. Then, at the 4 millionth event, we change the distribution type. We use an uniform distribution with lower bound $a=80$ and upper bound $b=120$. Note in Figure \ref{fig:timeseries-t5} that this last portion resembles the first one, the reference.
\begin{center}
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-r5.pdf}
  \captionof{figure}{Time-series for dataset R5}
  \label{fig:timeseries-r5}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/timeseries-t5.pdf}
  \captionof{figure}{Time-series for dataset T5}
  \label{fig:timeseries-t5}
\end{minipage}
\end{center}

Let's take a look at the signal computed for the target period. Figure \ref{fig:JSD-signal-test05} shows us the JSD signal for dataset T5 \ref{fig:timeseries-t5}. As expected, we see a rapid growth of JSD value after the 2 millionth event, when we change the Gaussian parameters. We then change the distribution type, from a gaussian to a uniform one. Despite the latter having a domain contained within the former, we see that our signal is accurate and does not drop below the alert threshold. This is still a different distribution that we want to alert. Figure \ref{fig:JSD-signal-zoom-test05} is a zoom in of the first 2 millionth events and once again we have no false positives.
\begin{figure}[!htb]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-test05.pdf}
  \captionof{figure}{JSD signal and threshold}
  \label{fig:JSD-signal-test05}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{figures/stream-analysis-viz-zoom-test05.pdf}
  \caption{Zoom in on the first 2 million events}
  \label{fig:JSD-signal-zoom-test05}
\end{subfigure}
\caption{JSD signal and threshold}
\end{figure}

@@

\begin{figure}[!htb] 
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-r6-x1.pdf} 
    \caption{Feature x1 reference time-series} 
    \label{fig:timeseries-r6-x1} 
    \vspace{4ex}
  \end{minipage}%%
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-r6-x2.pdf} 
    \caption{Feature x2 reference time-series} 
    \label{fig:timeseries-r6-x2} 
    \vspace{4ex}
  \end{minipage} 
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-r6-x3.pdf} 
    \caption{Feature x3 reference time-series} 
    \label{fig:timeseries-r6-x3} 
    \vspace{4ex}
  \end{minipage}%% 
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-r6-x4.pdf} 
    \caption{Feature x4 reference time-series} 
    \label{fig:timeseries-r6-x4} 
    \vspace{4ex}
  \end{minipage} 
\end{figure}

@@

\begin{figure}[!htb] 
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-t6-x1.pdf} 
    \caption{Feature x1 target time-series} 
    \label{fig:timeseries-t6-x1} 
    \vspace{4ex}
  \end{minipage}%%
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-t6-x2.pdf} 
    \caption{Feature x2 target time-series} 
    \label{fig:timeseries-t6-x2} 
    \vspace{4ex}
  \end{minipage} 
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-t6-x3.pdf} 
    \caption{Feature x3 target time-series} 
    \label{fig:timeseries-t6-x3} 
    \vspace{4ex}
  \end{minipage}%% 
  \begin{minipage}[b]{0.5\linewidth}
    \centering
    \includegraphics[width=1\linewidth]{figures/timeseries-t6-x4.pdf} 
    \caption{Feature x4 target time-series} 
    \label{fig:timeseries-t6-x4} 
    \vspace{4ex}
  \end{minipage} 
\end{figure}
